miniKanren with fair search strategies

### 2019-05-18 Paper/paper.tex
new DFSbi

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
in the \disj{} macro. We list the new \disj{} with its helpers in 
Fig.~\ref{balanced-disj}. The first helper function, \texttt{split}, takes a 
list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
into two sub-lists of roughly equal length, and returns the application of 
\texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
\texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
constructs a \emph{balanced} binary tree where leaves are elements of 
\texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
strategy. In contrast, the \disj{} in DFS$_\textrm{i}$ constructs the binary 
tree with the same collection of leaf nodes but in a particularly unbalanced 
form.

>>>>

Balanced interleaving DFS (DFS$_\textrm{bi}$) has almost-fair \disj{} and unfair 
\conj{}. The implementation of DFS$_\textrm{bi}$ differs from DFS$_\textrm{i}$ 
in the \disj{} macro. We list the new \disj{} with its helper in 
Fig.~\ref{balanced-disj}. The helper \code{disj+} builds a balanced binary tree 
whose leaves are the goals and whose nodes are \code{disj2}, hence the name of 
this search strategy. The first argument 
to \code{disj+} is the goals. And the next two arguments accumulate goals in 
the left and right subtrees. The first clause says that when there is one goal, 
the tree is the goal itself. When there is more goals, they are partitioned 
into two sub-lists. The partition is done by repetitively dispatch the first 
two goals (the last clause), until no goal remains (the second clause) or one 
goal remains (the third clause). In contrast, the \disj{} in DFS$_\textrm{i}$ 
constructs the binary tree with the same collection of leaf nodes but in a 
particularly unbalanced form.

% The first helper function, \texttt{split}, takes a 
% list of goals \texttt{ls} and a procedure \texttt{k}, partitions \texttt{ls} 
% into two sub-lists of roughly equal length, and returns the application of 
% \texttt{k} to the two sub-lists. \texttt{disj*} takes a non-empty list of goals 
% \texttt{gs} and returns a goal. With the help of \texttt{split}, it essentially 
% constructs a \emph{balanced} binary tree where leaves are elements of 
% \texttt{gs} and nodes are \texttt{disj2}s, hence the name of this search 
% strategy.
